---
title: "POLI666 Manual Replication - MASTER FILE"
author: "Leo Amorim, Aiden McIlvaney, and Alan Nemirovski"
date: "`r Sys.Date()`"
output: pdf_document
---

# Setup and data loading

```{r setup, warning = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r}
set.seed(666)

library(tidyverse)
library(haven)
library(lmtest)
library(sandwich)
library(modelsummary)
library(kableExtra)
library(psych)
library(lavaan)

data <- read_dta("moscowpopsurvey.dta", encoding = "Windows-1251")
```

# Cleaning data: Constructing variables

### Building three time periods
```{r}
data <- data %>% 
  rename(day = DATA) %>% 
  mutate(period = ifelse(day > 24 | day < 5, 1, 0),
         dec25 = ifelse(MONTH == 12 & day == 25, 1, 0),
         period1 = period - dec25,
         period2 = ifelse(day > 4 & day < 12, 1, 0),
         electday = ifelse(MONTH == 12 & day == 4, 1, 0),
         #electday = "Election Day"
         protestday = ifelse(MONTH == 12 & day == 10, 1, 0),
         #protestday = "Protest Day"
         period1min = period1 - electday,
         period2min = period2 - protestday,
         #period2min = "Post-Election"
         period3 = ifelse(day > 10 & day < 26 & MONTH == 12, 1, 0))
         #period3 = "Post-Protest"
```

### Building trust measures

```{r}
data <- data %>% 
  mutate(trustarmy = case_match(q9a, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                                .default = q9a), #Army
         trustpolice = case_match(q9b, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                                  .default = q9b), #Police
         trustfsb = case_match(q9c, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                               .default = q9c), #FSB
         trustcourt = case_match(q9d, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                                 .default = q9d), #Court
         trustmungov = case_match(q9e, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                                  .default = q9e), #City Gov't
         trustfedgov = case_match(q9f, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                                  .default = q9f), #Fed Gov't
         trustduma = case_match(q9g, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                                .default = q9g), #Duma
         trustprocuracy = case_match(q9h, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                                     .default = q9h), #Procuracy
         trustchurch = case_match(q9i, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                                  .default = q9i), #Church
         #Church was not included in the original paper's analysis, 
         #but is included here for subsequent analysis/checks.
         trustun = case_match(q9j, 99 ~ NA, 1 ~ 5, 2 ~ 4, 4 ~ 2, 5 ~ 1, 
                              .default = q9j)) #UN

#joining trust measures into gov trust index (trustgovind)

data <- data %>% 
  mutate(trustgovind = (trustarmy + trustpolice + trustfsb + trustcourt + 
                          trustmungov + trustfedgov + trustduma +
                          trustprocuracy)/8)
#Gov't Index (as built by Frye and Borisova 2019)
  
```

### Mapping out/recoding potential confounders

```{r}

data <- data %>% 
  rename(age = q1,
         male = q2,
         wealth = q3,
         education = q5,
         permres = q59,
         nationality = q67) %>% 
  mutate(male = ifelse(male == 2, 0, 1),
         wealth = case_match(wealth, 99 ~ NA, .default = wealth),
         education = case_match(education, 99 ~ NA, .default = education),
         permres = case_match(permres, 99 ~ NA, 2 ~ 0, 3 ~ 0, 
                              .default = permres),
       nationality = case_match(nationality, 2 ~ 0, 3 ~ 0, 4 ~ 0, 5 ~ 0,
                                6 ~ 0, 7 ~ 0, 8 ~ 0, 9 ~ 0, 10 ~ 0, 11 ~ 0,
                                99 ~ 0, .default = nationality),
       unemp = ifelse(q6 == 11 | q6 == 12 | q6 == 13, 1, 0),
       statesector = ifelse(q7 > 9 & q7 < 13, 1, 0),
       okrug = factor(okrug))

table(data$okrug)

```


### Coding partisanship

```{r}
#nesting each partisanship variable in its own mutate() function
#q62 = "Which party do you intend to vote for?"
#q64 = "Which party did you vote for in the previous election?"
data <- data %>% 
  mutate(urplan = 0, urturn = 0,
         urplan = ifelse(!is.na(q62) & q62 == 6, 1, 0),
         urturn = ifelse(!is.na(q64) & q64 == 6, 1, 0),
         ur = urplan + urturn) %>% #united russia variable
  mutate(complan = 0, compturn = 0,
         complan = ifelse(!is.na(q62) & q62 == 3, 1, 0),
         compturn = ifelse(!is.na(q64) & q64 == 3, 1, 0),
         comp = complan + compturn) %>% #CPFR party (?)
  mutate(ldprplan = 0, ldprturn = 0,
         ldprplan = ifelse(!is.na(q62) & q62 == 4, 1, 0),
         ldprturn = ifelse(!is.na(q64) & q64 == 4, 1, 0),
         ldpr = ldprplan + ldprturn) %>% #LDPR party
  mutate(yabplan = 0, yabturn = 0,
         yabplan = ifelse(!is.na(q62) & q62 == 1, 1, 0),
         yabturn = ifelse(!is.na(q64) & q64 == 1, 1, 0), #Yabloko party
         yab = yabplan + yabturn) %>% 
  mutate(patplan = 0, patturn = 0,
         patplan = ifelse(!is.na(q62) & q62 == 2, 1, 0),
         patturn = ifelse(!is.na(q64) & q64 == 2, 1, 0),
         pat = patplan + patturn) %>% #Unsure of party
  mutate(srplan = 0, srturn = 0,
         srplan = ifelse(!is.na(q62) & q62 == 5, 1, 0),
         srturn = ifelse(!is.na(q64) & q64 == 5, 1, 0),
         sr = srplan + srturn) %>% #Fair Russia party
  mutate(rcplan = 0, rcturn = 0,
         rcplan = ifelse(!is.na(q62) & q62 == 7, 1, 0),
         rcturn = ifelse(!is.na(q64) & q64 == 7, 1, 0),
         rc = rcplan + rcturn) %>% #Unsure of party
  mutate(dkplan = ifelse(!is.na(q62) & q62 == 99, 1, 0),
         dkturn = ifelse(!is.na(q64) & q64 == 99, 1, 0),
         dk = dkplan + dkturn) %>% #people who "don't know" (q62/q64 = 99)
  mutate(nopart = 0,
         nopart = ifelse((!is.na(q61) & q61 == 2) | (!is.na(q63) & q63 == 2) | 
                           (!is.na(q62) & q62 == 0), 1, 0)) #no party

#q61 = "Do you intend to vote in the upcoming (Duma) elections?"
#q63 = "Did you vote in the previous (Duma) elections?"

```


### Coding non-response variables

```{r}

data <- data %>% 
  mutate(trustgovind.nr = case_when(trustgovind >= 0.85 ~ 1, NA ~ 1, TRUE ~ 0),
         trustarmy.nr = case_match(q9a, 99 ~ 1, .default = 0),
         trustpolice.nr = case_match(q9b, 99 ~ 1, .default = 0),
         trustfsb.nr = case_match(q9c, 99 ~ 1, .default = 0),
         trustcourt.nr = case_match(q9d, 99 ~ 1, .default = 0),
         trustmungov.nr = case_match(q9e, 99 ~ 1, .default = 0),
         trustfedgov.nr = case_match(q9f, 99 ~ 1, .default = 0),
         trustduma.nr = case_match(q9g, 99 ~ 1, .default = 0),
         trustprocuracy.nr = case_match(q9h, 99 ~ 1, .default = 0),
         trustchurch.nr = case_match(q9i, 99 ~ 1, .default = 0),
         trustun.nr = case_match(q9j, 99 ~ 1, .default = 0))

```


# Results

### Table 1

```{r}
#period 1 vs. period 2
p12.data <- data %>% filter(period3 != 1 & electday != 1 & protestday !=1)

p12.army <- t.test(trustarmy ~ period1min, data = p12.data)
p12.police <- t.test(trustpolice ~ period1min, data = p12.data)
p12.fsb <- t.test(trustfsb ~ period1min, data = p12.data)
p12.court <- t.test(trustcourt ~ period1min, data = p12.data)
p12.mungov <- t.test(trustmungov ~ period1min, data = p12.data)
p12.fedgov <- t.test(trustfedgov ~ period1min, data = p12.data)
p12.duma <- t.test(trustduma ~ period1min, data = p12.data)
p12.procuracy <- t.test(trustprocuracy ~ period1min, data = p12.data)
p12.un <- t.test(trustun ~ period1min, data = p12.data)
p12.trustgovind <- t.test(trustgovind ~ period1min, data = p12.data)

```

```{r}
#period 1 vs. period 3
p13.data <- data %>% filter(period2min != 1 & electday != 1 & protestday !=1)

p13.army <- t.test(trustarmy ~ period1min, data = p13.data)
p13.police <- t.test(trustpolice ~ period1min, data = p13.data)
p13.fsb <- t.test(trustfsb ~ period1min, data = p13.data)
p13.court <- t.test(trustcourt ~ period1min, data = p13.data)
p13.mungov <- t.test(trustmungov ~ period1min, data = p13.data)
p13.fedgov <- t.test(trustfedgov ~ period1min, data = p13.data)
p13.duma <- t.test(trustduma ~ period1min, data = p13.data)
p13.procuracy <- t.test(trustprocuracy ~ period1min, data = p13.data)
p13.un <- t.test(trustun ~ period1min, data = p13.data)
p13.trustgovind <- t.test(trustgovind ~ period1min, data = p13.data)

```

```{r}
#period 2 vs. period 3
p23.data <- data %>% filter(period1min != 1 & electday != 1 & protestday !=1)

p23.army <- t.test(trustarmy ~ period2min, data = p23.data)
p23.police <- t.test(trustpolice ~ period2min, data = p23.data)
p23.fsb <- t.test(trustfsb ~ period2min, data = p23.data)
p23.court <- t.test(trustcourt ~ period2min, data = p23.data)
p23.mungov <- t.test(trustmungov ~ period2min, data = p23.data)
p23.fedgov <- t.test(trustfedgov ~ period2min, data = p23.data)
p23.duma <- t.test(trustduma ~ period2min, data = p23.data)
p23.procuracy <- t.test(trustprocuracy ~ period2min, data = p23.data)
p23.un <- t.test(trustun ~ period2min, data = p23.data)
p23.trustgovind <- t.test(trustgovind ~ period2min, data = p23.data)

```

### Table 2

```{r,  results = 'asis'}
#running all regression separately

lm.govindex <- lm(trustgovind ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.army <- lm(trustarmy ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.police <- lm(trustpolice ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.fsb <- lm(trustfsb ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.court <- lm(trustcourt ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.mungov <- lm(trustmungov ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.fedgov <- lm(trustfedgov ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.duma <- lm(trustduma ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.procuracy <- lm(trustprocuracy ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

lm.un <- lm(trustun ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data) 

#reporting in one table
modelsummary(list("Gov Index" = lm.govindex, "Army" = lm.army, "Police" = lm.police, 
                  "FSB" = lm.fsb, "Court" = lm.court, "Municipal Gov" = lm.mungov,
                  "Federal Gov" = lm.fedgov, "Duma" = lm.duma, 
                  "Procuracy" = lm.procuracy, "United Nations" = lm.un),
             title = "Determinants of trust in institutions",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
             "period2min" = "Post-election", "protestday" = "Protest day", 
             "electday" = "Election day"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))

```

## Extending measures of trust

### Including the Orthodox Church
```{r,  results = 'asis'}
data <- data %>% 
  mutate(trustgovind.withchurch = (trustarmy + trustpolice + trustfsb + trustcourt + 
                          trustmungov + trustfedgov + trustduma + trustprocuracy +
                            trustchurch)/9)

lm.indexwithchurch <- lm(trustgovind.withchurch ~ period3 + period2min + protestday + 
                           electday + wealth + education + okrug, data = data)

lm.church <- lm(trustchurch ~ period3 + period2min + protestday + electday + wealth + 
                  education + okrug, data = data)

#reporting in one table
modelsummary(list("Gov Index (with Church)" = lm.indexwithchurch, 
                  "Church" = lm.church),
             title = "Accounting for the role of Church",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
             "period2min" = "Post-election", "protestday" = "Protest day", 
             "electday" = "Election day"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))
```

### Leave-one-out indices
```{r, results = 'asis'}
data <- data %>% 
  mutate(trustgovind.noarmy = (trustpolice + trustfsb + trustcourt + trustmungov + 
                                 trustfedgov + trustduma + trustprocuracy)/7,
         trustgovind.nopolice = (trustarmy + trustfsb + trustcourt + trustmungov + 
                                 trustfedgov + trustduma + trustprocuracy)/7,
         trustgovind.nofsb = (trustpolice + trustarmy + trustcourt + trustmungov + 
                                 trustfedgov + trustduma + trustprocuracy)/7,
         trustgovind.nocourt = (trustpolice + trustfsb + trustarmy + trustmungov + 
                                 trustfedgov + trustduma + trustprocuracy)/7,
         trustgovind.nomungov = (trustpolice + trustfsb + trustcourt + trustarmy + 
                                 trustfedgov + trustduma + trustprocuracy)/7,
         trustgovind.nofedgov = (trustpolice + trustfsb + trustcourt + trustmungov + 
                                 trustarmy + trustduma + trustprocuracy)/7,
         trustgovind.noduma = (trustpolice + trustfsb + trustcourt + trustmungov + 
                                 trustfedgov + trustarmy + trustprocuracy)/7,
         trustgovind.noproc = (trustpolice + trustfsb + trustcourt + trustmungov + 
                                 trustfedgov + trustduma + trustarmy)/7)

lm.noarmy <- lm(trustgovind.noarmy ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data) 

lm.nopolice <- lm(trustgovind.nopolice ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data) 

lm.nofsb <- lm(trustgovind.nofsb ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data) 

lm.nocourt <- lm(trustgovind.nocourt ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data) 

lm.nomungov <- lm(trustgovind.nomungov ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data) 

lm.nofedgov <- lm(trustgovind.nofedgov ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data) 

lm.noduma <- lm(trustgovind.noduma ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data) 

lm.noproc <- lm(trustgovind.noproc ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data)

#reporting in one table
modelsummary(list("No Army" = lm.noarmy, "No Police" = lm.nopolice, 
                  "No FSB" = lm.nofsb, "No Court" = lm.nocourt, 
                  "No Municipal Gov" = lm.nomungov, "No Federal Gov" = lm.nofedgov, 
                  "No Duma" = lm.noduma, "No Procuracy" = lm.noproc),
             title = "Robustness check on Gov't Trust: Leave-one-out indices",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
             "period2min" = "Post-election", "protestday" = "Protest day", 
             "electday" = "Election day"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))

```

### Sub-indices (based on Schneider 2017)
```{r, results = 'asis'}
#model 1: fedgov + duma + mungov
data <- data %>% 
  mutate(alt.trust.index1 = (trustfedgov + trustduma + trustmungov)/3)

lm.alt1 <- lm(alt.trust.index1 ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data)

##NOTE: Schneider distinguishes between police and armed forces, but the role of
#the FSB seems ambiguous within that. for that reason, models 2-5 differentially
#include/exclude the FSB to see if that has any effect on results.

#model 2: fedgov + duma + police + army
data <- data %>% 
  mutate(alt.trust.index2 = (trustfedgov + trustduma + trustpolice + trustarmy)/4)

lm.alt2 <- lm(alt.trust.index2 ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data)

#model 3: fedgov + duma + police + army + fsb
data <- data %>% 
  mutate(alt.trust.index3 = (trustfedgov + trustduma + trustpolice + trustfsb +
                               trustarmy)/5)

lm.alt3 <- lm(alt.trust.index3 ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data)

#model 4: fedgov + duma + court + police
data <- data %>% 
  mutate(alt.trust.index4 = (trustfedgov + trustduma + trustpolice + trustcourt)/4)

lm.alt4 <- lm(alt.trust.index4 ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data)

#model 5: fedgov + duma + court + police + fsb
data <- data %>% 
  mutate(alt.trust.index5 = (trustfedgov + trustduma + trustpolice + trustcourt +
                               trustfsb)/4)

lm.alt5 <- lm(alt.trust.index5 ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data)

#reporting in one table
modelsummary(list("Model 1" = lm.alt1, "Model 2.1" = lm.alt2, 
                  "Model 2.2" = lm.alt3, 
                  "Model 3.1" = lm.alt4, 
                  "Model 3.2" = lm.alt5),
             title = "Robustness check on Gov't Trust: Alternative sub-indices",
             caption = "Sub-indices constructed following Schneider (2017)",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
             "period2min" = "Post-election", "protestday" = "Protest day", 
             "electday" = "Election day"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             add_rows = tribble(
               ~term, ~"Model 1", ~"Model 2.1", ~"Model 2.2", ~"Model 3.1", ~"Model 3.2",
               "Fed Gov", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Duma", "Yes", "Yes", "Yes", "Yes", "Yes",
               "Mun Gov", "Yes", " ", " ", " ", " ",
               "Police", " ", "Yes", "Yes", "Yes", "Yes",
               "Army", " ", "Yes", "Yes", " ", " ",
               "Court", " ", " ", " ", "Yes", "Yes",
               "FSB", " ", " ", "Yes", " ", "Yes"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))

```


### Standardized index
```{r}

data <- data %>% 
  mutate(trustarmy.z = as.numeric(scale(trustarmy)),
         trustpolice.z = as.numeric(scale(trustpolice)),
         trustfsb.z = as.numeric(scale(trustfsb)),
         trustcourt.z = as.numeric(scale(trustcourt)),
         trustmungov.z = as.numeric(scale(trustmungov)),
         trustfedgov.z = as.numeric(scale(trustfedgov)),
         trustduma.z = as.numeric(scale(trustduma)),
         trustprocuracy.z = as.numeric(scale(trustprocuracy)),
         trustgovindex.standardized = (trustarmy.z + trustpolice.z + trustfsb.z +
                                         trustcourt.z + trustmungov.z + trustfedgov.z +
                                         trustduma.z + trustprocuracy.z)/8)

lm.standardized <- lm(trustgovindex.standardized ~ period3 + period2min + protestday + 
                           electday + wealth + education + okrug, data = data)

modelsummary(lm.standardized,
             title = "Robustness check on Gov't Trust: Index with Z-Scored Items",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
             "period2min" = "Post-election", "protestday" = "Protest day", 
             "electday" = "Election day"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))

```

### Factor-score index
```{r, results = 'asis'}
#Factor loading analysis
fa.analysis.data <- data %>% 
  select(trustarmy, trustpolice, trustfsb, trustcourt, trustmungov,
         trustfedgov, trustduma, trustprocuracy)

fa.fit <- fa(fa.analysis.data, nfactors = 1, rotate = "oblimin", fm = "ml")

fa.parallel(fa.analysis.data, fm = "ml")
cr.alpha.data <- alpha(fa.analysis.data) 
#crohnback's alpha ~ 0.903
data.frame(raw_alpha = cr.alpha.data$total$raw_alpha,
           std.alpha = cr.alpha.data$total$std.alpha)

#Factor-score-weighted index
fa.fit$loadings
weights <- as.numeric(fa.fit$loadings)
weights.norm <- weights/sum(weights)
weights.norm

data <- data %>% 
  mutate(trustgovind.factor.weight = (0.091*trustarmy) + (0.119*trustpolice) +
           (0.121*trustfsb) + (0.117*trustcourt) + (0.141*trustmungov) + 
           (0.146*trustfedgov) + (0.141*trustduma) + (0.124*trustprocuracy))
#all weights add up to 1

lm.factor.weighted <- lm(trustgovind.factor.weight ~ period3 + period2min + protestday + 
                           electday + wealth + education + okrug, data = data)

modelsummary(lm.factor.weighted,
             title = "Robustness check on Gov't Trust: Factor Loading Score-Weighted Index",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
             "period2min" = "Post-election", "protestday" = "Protest day", 
             "electday" = "Election day"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))

```

```{r}
#additional confirmatory factor analysis
model <- "trust =~ trustarmy + trustpolice + trustfsb + trustcourt +
                   trustmungov + trustfedgov + trustduma + trustprocuracy"

model.fit <- cfa(model, data = data)
summary(model.fit, fit.measures = TRUE)

##Comparative fit measurements - closer to 1 the better
#CFI: 0.822
#TLI: 0.75

#RMSEA: 0.217 (penalized model complexity)
#SRMR: 0.09 (difference between observed and model-implied correlations)

#NOTE: Borderline/poorer statistics more common with survey data (sensitive to N).

```

# Mechanisms

### Figure 1

```{r}

data <- data %>% 
  mutate(period123 = case_when(period1min == 1 ~ 1,
                               period2min == 1 ~ 2,
                               period3 == 1 ~ 3,
                               TRUE ~ NA_real_),
         opposition = yab + pat + sr + rc,
         party = case_when(ur == 1 ~ 1,
                           comp == 1 ~ 2,
                           ldpr == 1 ~ 3,
                           opposition == 1 ~ 4,
                           nopart == 1 ~ 5,
                           dk == 1 ~ 6,
                           TRUE ~ 0),
         partynames = case_when(party == 1 ~ "UR",
                                party == 2 ~ "CPRF",
                                party == 3 ~ "LDPR",
                                party == 4 ~ "Opposition",
                                party == 5 ~ "Non-voters",
                                party == 6 ~ "Undecided",
                                TRUE ~ NA_character_),
         partynames = factor(partynames)) %>%
  mutate(trustgovind1 = ifelse(period1min == 1, 1, 0),
         trustgovind2 = ifelse(period2min == 1, 1, 0),
         trustgovind3 = ifelse(period3 == 1, 1, 0))

data %>%
  group_by(partynames, period123) %>%
  summarize(mean.trust = mean(trustgovind, na.rm = TRUE)) %>% 
  ungroup() %>%
  ggplot(aes(x = partynames, 
             y = mean.trust, 
             fill = factor(period123))) +
  geom_col(position = "dodge") +
  labs(y = "Trust in Government Index", fill = "Period")
```


### Table 3

```{r, result = 'asis'}

data <- data %>% 
  mutate(urafterprotest = ur*period3,
         urpostelection = ur*period2min,
         apolitical = nopart + dk,
         apolafterprotest = apolitical*period3,
         apolpostelection = apolitical*period2min)

lm.interact.govindex <- lm(trustgovind ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.army <- lm(trustarmy ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.police <- lm(trustpolice ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.fsb <- lm(trustfsb ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.court <- lm(trustcourt ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.mungov <- lm(trustmungov ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.fedgov <- lm(trustfedgov ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.duma <- lm(trustduma ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.procuracy <- lm(trustprocuracy ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data) 

lm.interact.un <- lm(trustun ~ period3 + period2min + protestday + electday + 
                                ur + urafterprotest + urpostelection + 
                                apolitical + apolafterprotest + apolpostelection +
                                wealth + education + okrug, data = data)

modelsummary(list("Gov Index" = lm.interact.govindex, "Army" = lm.interact.army, "Police" = lm.interact.police, 
                  "FSB" = lm.interact.fsb, "Court" = lm.interact.court, "Municipal Gov" = lm.interact.mungov,
                  "Federal Gov" = lm.interact.fedgov, "Duma" = lm.interact.duma, 
                  "Procuracy" = lm.interact.procuracy, "United Nations" = lm.interact.un),
             title = "Determinants of trust in institutions",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
             "period2min" = "Post-election", "protestday" = "Protest day", 
             "electday" = "Election day", "ur" = "United Russia", "urafterprotest" = "United Russia x Post-Protest", "urpostelection" = "United Russia x Post-Election", "apolitical" = "Apolitical", "apolafterprotest" = "Apolitical x Post-Protest", "apolafterelection" = "Apolitical x Post-Election"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))


```


### Figure 2

```{r}

vcov.fig2 <- coeftest(lm.interact.govindex, vcov = vcovHC(lm.interact.govindex, type = "HC2"))

vars <- c("period3", "period2min", "protestday", "electday", "ur", "urafterprotest", "urpostelection", "apolitical", "apolafterprotest", "apolpostelection")
var.names <- c("period3" = "Post-Protest",
               "period2min" = "Post-Election",
               "protestday" = "Protest Day",
               "electday" = "Election Day",
               "ur" = "United Russia",
               "urafterprotest" = "United Russia x Post-Protest",
               "urpostelection" = "United Russia x Post-Election",
               "apolitical" = "Apolitical",
               "apolafterprotest" = "Apolitical x Post-Protest",
               "apolpostelection" = "Apolitical x Post-Election")

margeffects.data <- data.frame(vars = vars,
                               beta = vcov.fig2[vars, "Estimate"],
                               se = vcov.fig2[vars, "Std. Error"])

margeffects.data <- margeffects.data %>% 
  mutate(ci.lower = beta - 1.96 * se,
         ci.upper = beta + 1.96 * se,
         var.label = factor(var.names[vars]))

ggplot(margeffects.data, aes(x = beta, y = var.label)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
  geom_errorbar(aes(xmin = ci.lower, xmax = ci.upper), height = 0.2) +
  scale_y_discrete(limits = rev) +
  labs(x = "Marginal Effect on Trust in Government (Index)")

```


# Appendices

### Appendix I: (Balance test:) Distribution of respondents across districts by periods

```{r}
## Period 1 vs. Period 2 test without electday and protestday variables

balance.data1a <- data %>%
  filter(period3 != 1, electday != 1, protestday != 1)

t1.1a <- t.test(balance.data1a$okrug == 1 ~ balance.data1a$period1min, var.equal = TRUE)
t1.2a <- t.test(balance.data1a$okrug == 2 ~ balance.data1a$period1min, var.equal = TRUE)
t1.3a <- t.test(balance.data1a$okrug == 3 ~ balance.data1a$period1min, var.equal = TRUE)
t1.4a <- t.test(balance.data1a$okrug == 4 ~ balance.data1a$period1min, var.equal = TRUE)
t1.5a <- t.test(balance.data1a$okrug == 5 ~ balance.data1a$period1min, var.equal = TRUE)
t1.6a <- t.test(balance.data1a$okrug == 6 ~ balance.data1a$period1min, var.equal = TRUE)
t1.7a <- t.test(balance.data1a$okrug == 7 ~ balance.data1a$period1min, var.equal = TRUE)
t1.8a <- t.test(balance.data1a$okrug == 8 ~ balance.data1a$period1min, var.equal = TRUE)
t1.9a <- t.test(balance.data1a$okrug == 9 ~ balance.data1a$period1min, var.equal = TRUE)
t1.10a <- t.test(balance.data1a$okrug == 10 ~ balance.data1a$period1min, var.equal = TRUE)

tests.1a <- list(t1.1a, t1.2a, t1.3a, t1.4a, t1.5a, t1.6a, t1.7a, t1.8a, t1.9a, t1.10a)

balance.tab1a <- data.frame(district = paste0("okrug", 1:10),
                              mean.period2 = sapply(tests.1a, function(x) x$estimate[1]),
                              mean.period1 = sapply(tests.1a, function(x) x$estimate[2]),
                              diff = sapply(tests.1a, 
                                            function(x) x$estimate[2] - x$estimate[1]),
                              t.stat = sapply(tests.1a, function(x) x$statistic),
                              p.val = sapply(tests.1a, function(x) x$p.value),
                              row.names = NULL)

balance.tab1a

```

```{r}
## Period 1 vs. Period 3 test without electday and protestday variables

balance.data1b <- data %>%
  filter(period2min != 1, electday != 1, protestday != 1)

t1.1b <- t.test(balance.data1b$okrug == 1 ~ balance.data1b$period1min, var.equal = TRUE)
t1.2b <- t.test(balance.data1b$okrug == 2 ~ balance.data1b$period1min, var.equal = TRUE)
t1.3b <- t.test(balance.data1b$okrug == 3 ~ balance.data1b$period1min, var.equal = TRUE)
t1.4b <- t.test(balance.data1b$okrug == 4 ~ balance.data1b$period1min, var.equal = TRUE)
t1.5b <- t.test(balance.data1b$okrug == 5 ~ balance.data1b$period1min, var.equal = TRUE)
t1.6b <- t.test(balance.data1b$okrug == 6 ~ balance.data1b$period1min, var.equal = TRUE)
t1.7b <- t.test(balance.data1b$okrug == 7 ~ balance.data1b$period1min, var.equal = TRUE)
t1.8b <- t.test(balance.data1b$okrug == 8 ~ balance.data1b$period1min, var.equal = TRUE)
t1.9b <- t.test(balance.data1b$okrug == 9 ~ balance.data1b$period1min, var.equal = TRUE)
t1.10b <- t.test(balance.data1b$okrug == 10 ~ balance.data1b$period1min, var.equal = TRUE)

tests.1b <- list(t1.1b, t1.2b, t1.3b, t1.4b, t1.5b, t1.6b, t1.7b, t1.8b, t1.9b, t1.10b)

balance.tab1b <- data.frame(district = paste0("okrug", 1:10),
                              mean.period3 = sapply(tests.1b, function(x) x$estimate[1]),
                              mean.period1 = sapply(tests.1b, function(x) x$estimate[2]),
                              diff = sapply(tests.1b, 
                                            function(x) x$estimate[2] - x$estimate[1]),
                              t.stat = sapply(tests.1b, function(x) x$statistic),
                              p.val = sapply(tests.1b, function(x) x$p.value),
                              row.names = NULL)

balance.tab1b

```

```{r}
## Period 2 vs. Period 3 test without electday and protestday variables

balance.data1c <- data %>%
  filter(period1min != 1, electday != 1, protestday != 1)

t1.1c <- t.test(balance.data1c$okrug == 1 ~ balance.data1c$period3, var.equal = TRUE)
t1.2c <- t.test(balance.data1c$okrug == 2 ~ balance.data1c$period3, var.equal = TRUE)
t1.3c <- t.test(balance.data1c$okrug == 3 ~ balance.data1c$period3, var.equal = TRUE)
t1.4c <- t.test(balance.data1c$okrug == 4 ~ balance.data1c$period3, var.equal = TRUE)
t1.5c <- t.test(balance.data1c$okrug == 5 ~ balance.data1c$period3, var.equal = TRUE)
t1.6c <- t.test(balance.data1c$okrug == 6 ~ balance.data1c$period3, var.equal = TRUE)
t1.7c <- t.test(balance.data1c$okrug == 7 ~ balance.data1c$period3, var.equal = TRUE)
t1.8c <- t.test(balance.data1c$okrug == 8 ~ balance.data1c$period3, var.equal = TRUE)
t1.9c <- t.test(balance.data1c$okrug == 9 ~ balance.data1c$period3, var.equal = TRUE)
t1.10c <- t.test(balance.data1c$okrug == 10 ~ balance.data1c$period3, var.equal = TRUE)

tests.1c <- list(t1.1c, t1.2c, t1.3c, t1.4c, t1.5c, t1.6c, t1.7c, t1.8c, t1.9c, t1.10c)

balance.tab1c <- data.frame(district = paste0("okrug", 1:10),
                              mean.period2 = sapply(tests.1c, function(x) x$estimate[1]),
                              mean.period3 = sapply(tests.1c, function(x) x$estimate[2]),
                              diff = sapply(tests.1c, 
                                            function(x) x$estimate[2] - x$estimate[1]),
                              t.stat = sapply(tests.1c, function(x) x$statistic),
                              p.val = sapply(tests.1c, function(x) x$p.value),
                              row.names = NULL)

balance.tab1c

```


### Appendix II: (Balance tests:) Pre-treatment covariates

```{r}

## Period 1 vs. Period 2 test without electday and protestday variables

t2a.age <- t.test(balance.data1a$age ~ balance.data1a$period1min, var.equal = TRUE)
t2a.male <- t.test(balance.data1a$male ~ balance.data1a$period1min, var.equal = TRUE)
t2a.educ <- t.test(balance.data1a$education ~ balance.data1a$period1min, var.equal = TRUE)
t2a.wealth <- t.test(balance.data1a$wealth ~ balance.data1a$period1min, var.equal = TRUE)
t2a.permres <- t.test(balance.data1a$permres ~ balance.data1a$period1min, var.equal = TRUE)
t2a.nationality <- t.test(balance.data1a$nationality ~ balance.data1a$period1min, var.equal = TRUE)
t2a.unemp <- t.test(balance.data1a$unemp ~ balance.data1a$period1min, var.equal = TRUE)
t2a.statesector <- t.test(balance.data1a$statesector ~ balance.data1a$period1min, var.equal = TRUE)
t2a.ur <- t.test(balance.data1a$ur ~ balance.data1a$period1min, var.equal = TRUE)
t2a.comp <- t.test(balance.data1a$comp ~ balance.data1a$period1min, var.equal = TRUE)
t2a.opposition <- t.test(balance.data1a$opposition ~ balance.data1a$period1min, var.equal = TRUE)

tests.2a <- list(age = t2a.age, male = t2a.male, education = t2a.educ, wealth = t2a.wealth, permres = t2a.permres, nationality = t2a.nationality, unemployment = t2a.unemp, statesector = t2a.statesector, ur = t2a.ur, comp = t2a.comp, opposition = t2a.opposition)

balance.tab2a <- data.frame(var.name = names(tests.2a),
                            mean.period2 = sapply(tests.2a, function(x) x$estimate[1]),
                            mean.period1 = sapply(tests.2a, function(x) x$estimate[2]),
                            diff = sapply(tests.2a, 
                                          function(x) x$estimate[2] - x$estimate[1]),
                            t.stat = sapply(tests.2a, function(x) x$statistic),
                            p.val = sapply(tests.2a, function(x) x$p.value),
                            row.names = NULL)

balance.tab2a

```

```{r}

## Period 1 vs. Period 3 test without electday and protestday variables

t2b.age <- t.test(balance.data1b$age ~ balance.data1b$period1min, var.equal = TRUE)
t2b.male <- t.test(balance.data1b$male ~ balance.data1b$period1min, var.equal = TRUE)
t2b.educ <- t.test(balance.data1b$education ~ balance.data1b$period1min, var.equal = TRUE)
t2b.wealth <- t.test(balance.data1b$wealth ~ balance.data1b$period1min, var.equal = TRUE)
t2b.permres <- t.test(balance.data1b$permres ~ balance.data1b$period1min, var.equal = TRUE)
t2b.nationality <- t.test(balance.data1b$nationality ~ balance.data1b$period1min, var.equal = TRUE)
t2b.unemp <- t.test(balance.data1b$unemp ~ balance.data1b$period1min, var.equal = TRUE)
t2b.statesector <- t.test(balance.data1b$statesector ~ balance.data1b$period1min, var.equal = TRUE)
t2b.ur <- t.test(balance.data1b$ur ~ balance.data1b$period1min, var.equal = TRUE)
t2b.comp <- t.test(balance.data1b$comp ~ balance.data1b$period1min, var.equal = TRUE)
t2b.opposition <- t.test(balance.data1b$opposition ~ balance.data1b$period1min, var.equal = TRUE)

tests.2b <- list(age = t2b.age, male = t2b.male, education = t2b.educ, wealth = t2b.wealth, permres = t2b.permres, nationality = t2b.nationality, unemployment = t2b.unemp, statesector = t2b.statesector, ur = t2b.ur, comp = t2b.comp, opposition = t2b.opposition)

balance.tab2b <- data.frame(var.name = names(tests.2b),
                            mean.period3 = sapply(tests.2b, function(x) x$estimate[1]),
                            mean.period1 = sapply(tests.2b, function(x) x$estimate[2]),
                            diff = sapply(tests.2b, 
                                          function(x) x$estimate[2] - x$estimate[1]),
                            t.stat = sapply(tests.2b, function(x) x$statistic),
                            p.val = sapply(tests.2b, function(x) x$p.value),
                            row.names = NULL)

balance.tab2b

```

```{r}

## Period 2 vs. Period 3 test without electday and protestday variables

t2c.age <- t.test(balance.data1c$age ~ balance.data1c$period3, var.equal = TRUE)
t2c.male <- t.test(balance.data1c$male ~ balance.data1c$period3, var.equal = TRUE)
t2c.educ <- t.test(balance.data1c$education ~ balance.data1c$period3, var.equal = TRUE)
t2c.wealth <- t.test(balance.data1c$wealth ~ balance.data1c$period3, var.equal = TRUE)
t2c.permres <- t.test(balance.data1c$permres ~ balance.data1c$period3, var.equal = TRUE)
t2c.nationality <- t.test(balance.data1c$nationality ~ balance.data1c$period3, var.equal = TRUE)
t2c.unemp <- t.test(balance.data1c$unemp ~ balance.data1c$period3, var.equal = TRUE)
t2c.statesector <- t.test(balance.data1c$statesector ~ balance.data1c$period3, var.equal = TRUE)
t2c.ur <- t.test(balance.data1c$ur ~ balance.data1c$period3, var.equal = TRUE)
t2c.comp <- t.test(balance.data1c$comp ~ balance.data1c$period3, var.equal = TRUE)
t2c.opposition <- t.test(balance.data1c$opposition ~ balance.data1c$period3, var.equal = TRUE)

tests.2c <- list(age = t2c.age, male = t2c.male, education = t2c.educ, wealth = t2c.wealth, permres = t2c.permres, nationality = t2c.nationality, unemployment = t2c.unemp, statesector = t2c.statesector, ur = t2c.ur, comp = t2c.comp, opposition = t2c.opposition)

balance.tab2c <- data.frame(var.name = names(tests.2c),
                            mean.period2 = sapply(tests.2c, function(x) x$estimate[1]),
                            mean.period3 = sapply(tests.2c, function(x) x$estimate[2]),
                            diff = sapply(tests.2c, 
                                          function(x) x$estimate[2] - x$estimate[1]),
                            t.stat = sapply(tests.2c, function(x) x$statistic),
                            p.val = sapply(tests.2c, function(x) x$p.value),
                            row.names = NULL)

balance.tab2c

```

### Appendix III: Differences in partisanship across periods

```{r}

plot.app3.data <- data %>%
  group_by(period123) %>%
  summarize(UR = mean(ur, na.rm = TRUE), 
            CPRF = mean(comp, na.rm = TRUE),
            LDPR = mean(ldpr, na.rm = TRUE), 
            Opposition = mean(opposition, na.rm = TRUE),
            Undecided  = mean(dk, na.rm = TRUE)) %>%
  ungroup() %>% 
  pivot_longer(cols = -period123, names_to = "party.name", values_to = "share") %>%
  mutate(party.name = factor(party.name, 
                             levels = c("UR", "CPRF", "LDPR", "Opposition", "Undecided")),
         period.name = factor(period123, levels = c(1, 2, 3),
                              labels = c("Pre-Election", "Post-Election", "Post-Protest")))

ggplot(plot.app3.data, aes(x = party.name, y = share, fill = period.name)) +
  geom_col(position = "dodge") +
  labs(x = NULL, y = "Proportion of Respondents", fill = "Period")

```


### Appendix IV: Non-responses

```{r}

## Period 1 vs. Period 2 test (without electday and protestday variables)

t3a.trustgovind <- t.test(balance.data1a$trustgovind.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustarmy <- t.test(balance.data1a$trustarmy.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustpolice <- t.test(balance.data1a$trustpolice.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustfsb <- t.test(balance.data1a$trustfsb.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustcourt <- t.test(balance.data1a$trustcourt.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustmungov <- t.test(balance.data1a$trustmungov.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustfedgov <- t.test(balance.data1a$trustfedgov.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustduma <- t.test(balance.data1a$trustduma.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustprocuracy <- t.test(balance.data1a$trustprocuracy.nr ~ balance.data1a$period1min, var.equal = TRUE)
t3a.trustun <- t.test(balance.data1a$trustun.nr ~ balance.data1a$period1min, var.equal = TRUE)

tests.3a <- list(gov.index = t3a.trustgovind, army = t3a.trustarmy, police = t3a.trustpolice, fsb = t3a.trustfsb, court = t3a.trustcourt, mun.gov = t3a.trustmungov, fed.gov = t3a.trustfedgov, duma = t3a.trustduma, procuracy = t3a.trustprocuracy, un = t3a.trustun)

balance.tab3a <- data.frame(var.name = names(tests.3a),
                            mean.period2 = sapply(tests.3a, function(x) x$estimate[1]),
                            mean.period1 = sapply(tests.3a, function(x) x$estimate[2]),
                            diff = sapply(tests.3a, 
                                          function(x) x$estimate[2] - x$estimate[1]),
                            t.stat = sapply(tests.3a, function(x) x$statistic),
                            p.val = sapply(tests.3a, function(x) x$p.value),
                            row.names = NULL)

balance.tab3a

```

```{r}

## Period 1 vs. Period 3 test (without electday and protestday variables)

t3b.trustgovind <- t.test(balance.data1b$trustgovind.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustarmy <- t.test(balance.data1b$trustarmy.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustpolice <- t.test(balance.data1b$trustpolice.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustfsb <- t.test(balance.data1b$trustfsb.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustcourt <- t.test(balance.data1b$trustcourt.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustmungov <- t.test(balance.data1b$trustmungov.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustfedgov <- t.test(balance.data1b$trustfedgov.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustduma <- t.test(balance.data1b$trustduma.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustprocuracy <- t.test(balance.data1b$trustprocuracy.nr ~ balance.data1b$period1min, var.equal = TRUE)
t3b.trustun <- t.test(balance.data1b$trustun.nr ~ balance.data1b$period1min, var.equal = TRUE)

tests.3b <- list(gov.index = t3b.trustgovind, army = t3b.trustarmy, police = t3b.trustpolice, fsb = t3b.trustfsb, court = t3b.trustcourt, mun.gov = t3b.trustmungov, fed.gov = t3b.trustfedgov, duma = t3b.trustduma, procuracy = t3b.trustprocuracy, un = t3b.trustun)

balance.tab3b <- data.frame(var.name = names(tests.3b),
                            mean.period3 = sapply(tests.3b, function(x) x$estimate[1]),
                            mean.period1 = sapply(tests.3b, function(x) x$estimate[2]),
                            diff = sapply(tests.3b, 
                                          function(x) x$estimate[2] - x$estimate[1]),
                            t.stat = sapply(tests.3b, function(x) x$statistic),
                            p.val = sapply(tests.3b, function(x) x$p.value),
                            row.names = NULL)

balance.tab3b

```

```{r}

## Period 2 vs. Period 3 test (without electday and protestday variables)

t3c.trustgovind <- t.test(balance.data1c$trustgovind.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustarmy <- t.test(balance.data1c$trustarmy.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustpolice <- t.test(balance.data1c$trustpolice.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustfsb <- t.test(balance.data1c$trustfsb.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustcourt <- t.test(balance.data1c$trustcourt.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustmungov <- t.test(balance.data1c$trustmungov.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustfedgov <- t.test(balance.data1c$trustfedgov.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustduma <- t.test(balance.data1c$trustduma.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustprocuracy <- t.test(balance.data1c$trustprocuracy.nr ~ balance.data1c$period3, var.equal = TRUE)
t3c.trustun <- t.test(balance.data1c$trustun.nr ~ balance.data1c$period3, var.equal = TRUE)

tests.3c <- list(gov.index = t3c.trustgovind, army = t3c.trustarmy, police = t3c.trustpolice, fsb = t3c.trustfsb, court = t3c.trustcourt, mun.gov = t3c.trustmungov, fed.gov = t3c.trustfedgov, duma = t3c.trustduma, procuracy = t3c.trustprocuracy, un = t3c.trustun)

balance.tab3c <- data.frame(var.name = names(tests.3c),
                            mean.period2 = sapply(tests.3c, function(x) x$estimate[1]),
                            mean.period3 = sapply(tests.3c, function(x) x$estimate[2]),
                            diff = sapply(tests.3c, 
                                          function(x) x$estimate[2] - x$estimate[1]),
                            t.stat = sapply(tests.3c, function(x) x$statistic),
                            p.val = sapply(tests.3c, function(x) x$p.value),
                            row.names = NULL)

balance.tab3c

```

### Appendix V: Daily responses

```{r}
data <- data %>%
  mutate(time.trend = case_when(MONTH == 11 ~ day - 24,
                                MONTH == 12 ~ day + 6),
         date = case_when(MONTH == 11 ~ paste0("nov", day),
                         MONTH == 12 ~ paste0("dec", day)),
         date = factor(date, levels = c(paste0("nov", 25:30), paste0("dec", 1:24))),
         date = relevel(date, ref = "dec4"))

trend.reg <- lm(trustgovind ~ date + education + wealth, data = data)
vcov.trend.coefs <- coeftest(trend.reg, vcov = vcovHC(trend.reg, type = "HC2"))

dates.to.keep <- paste0("datedec", 5:24)
trend.plot.data <- data.frame(day = paste0("dec", 5:24),
                              beta = vcov.trend.coefs[dates.to.keep, "Estimate"],
                              se = vcov.trend.coefs[dates.to.keep, "Std. Error"]) %>% 
  mutate(ci.lower  = beta - 1.96 * se,
         ci.upper = beta + 1.96 * se)

ggplot(trend.plot.data, aes(x = beta, y = day)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
  geom_point(size = 2.5) +
  geom_errorbar(aes(xmin = ci.lower, xmax = ci.upper), height = 0.2) +
  labs(x = "Effect on Trust in Government (vs. Dec 4)", y = "Date")

```

# Online appendices

### Data manipulation

```{r}
#building individual-level meeting index

data <- data %>%
  mutate(invite1 = case_match(q57a, 99 ~ NA, 2 ~ 0, .default = q57a),
         invite2 = case_match(q57b, 99 ~ NA, 2 ~ 0, .default = q57b),
         invite3 = case_match(q57c, 99 ~ NA, 2 ~ 0, .default = q57c),
         invite.index = invite1 + invite2 + invite3,
         invite.index.names = case_match(invite.index,
                                         invite1 ~ "Meeting 1",
                                         invite2 ~ "Meeting 2",
                                         invite3 ~ "Meeting 3",
                                         .default = NA_character_))

```


### Online Appendix 1

```{r}

table(data$day, data$MONTH)

```


### Online Appendix 2

```{r, results='asis'}
#Table 2A: Determinants of trust in institutions
## Each trust measure's f-test is manually calculated out because it's difficult to put everything into one table - only one version of the code is included for brevity (but you would theoretically substitute "trustgovind" for any trust measure and rerun the chunk)

reg.appendix.2a <- lm(trustgovind ~ period3 + period2min + protestday + electday +
                        wealth + education + okrug, data = data)

vcov.tab2a <- vcovHC(reg.appendix.2a, type = "HC2")
coefs.tab2a <- coef(reg.appendix.2a)

#F-test
diff.beta <- coefs.tab2a["period2min"] - coefs.tab2a["period3"]
diff.var <- vcov.tab2a["period2min", "period2min"] + 
  vcov.tab2a["period3", "period3"] - 2*vcov.tab2a["period2min", "period3"]

F.stat <- (diff.beta^2) / diff.var
p.val <- pf(F.stat, df1 = 1, df2 = reg.appendix.2a$df.residual, lower.tail = FALSE)

#Table: Government trust index
modelsummary(list("Model" = reg.appendix.2a),
             vcov = "HC2",
             coef_map = c("period3" = "Post-Protest",
                          "period2min" = "Post-Election",
                          "protestday" = "Protest Day",
                          "electday"   = "Election Day"),
             title = "Table 2A: Determinants of trust in institutions",
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             add_rows = tribble(~term, ~Model,
                      "F-test", sprintf("%.2f", F.stat),
                      "F-test p-value",  sprintf("%.3f", p.val)),
             output = "kableExtra") %>% 
  kable_styling(latex_options = c("scale_down", "hold_position"))

```


```{r, results='asis'}
#Table 2A (with opposition voters getting information from TV)

reg2a.subset.data <- data %>% 
  filter(q30_2 == 1, ur == 0)

reg2a.subset.index <- lm(trustgovind ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.army <- lm(trustarmy ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.police <- lm(trustpolice ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.fsb <- lm(trustfsb ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.court <- lm(trustcourt ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.mungov <- lm(trustmungov ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.fedgov <- lm(trustfedgov ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.duma <- lm(trustduma ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.procuracy <- lm(trustprocuracy ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

reg2a.subset.un <- lm(trustun ~ period3 + period2min + protestday + electday +
    wealth + education + okrug, data = reg2a.subset.data)

#Table: Government trust index
modelsummary(list("Gov't Trust Index" = reg2a.subset.index, "Army" = reg2a.subset.army, "Police" = reg2a.subset.police, "FSB" = reg2a.subset.fsb, "Court" = reg2a.subset.court, "Mun. Gov" = reg2a.subset.mungov, "Fed. Gov" = reg2a.subset.fedgov, "Duma" = reg2a.subset.duma, "Procuracy" = reg2a.subset.procuracy, "UN" = reg2a.subset.un),
             vcov = "HC2",
             coef_map = c("period3" = "Post-Protest",
                          "period2min" = "Post-Election",
                          "protestday" = "Protest Day",
                          "electday" = "Election Day"),
             title = "Table 2A (with opposition voters getting information from TV)",
             stars = TRUE, fmt = 2, gof_map  = c("nobs", "r.squared"),
             output = "kableExtra")  %>% 
  kable_styling(latex_options = c("scale_down", "hold_position"))
```

```{r, results='asis'}
#Table 2B: Partisan impact of the election and protest on trust
## Each trust measure's f-test is manually calculated out because it's difficult to put everything into one table - only one version of the code is included for brevity (but you would theoretically substitute "trustgovind" for any trust measure and rerun the chunk)

reg.appendix.2b <- lm(trustgovind ~ period3 + period2min + protestday + electday +
                        ur + urafterprotest + urpostelection +
                        apolitical + apolafterprotest + apolpostelection +
                        wealth + education + okrug,data = data)

vcov.tab2b  <- vcovHC(reg.appendix.2b, type = "HC2")
coefs.tab2b <- coef(reg.appendix.2b)

#F-test
diff.beta <- coefs.tab2b["period2min"] - coefs.tab2b["period3"]
diff.var <- vcov.tab2b["period2min", "period2min"] +
  vcov.tab2b["period3", "period3"] - 2 * vcov.tab2b["period2min", "period3"]

F.stat <- (diff.beta^2) / diff.var
p.val <- pf(F.stat, df1 = 1, df2 = reg.appendix.2b$df.residual, lower.tail = FALSE)

#Table: Government Trust Index
modelsummary(list("Model" = reg.appendix.2b),
             vcov = "HC2",
             coef_map = c("period3" = "Post-Protest",
                          "period2min" = "Post-Election",
                          "protestday" = "Protest Day",
                          "electday" = "Election Day",
                          "ur" = "United Russia",
                          "urafterprotest" = "United Russia x Post-Protest",
                          "urpostelection" = "United Russia x Post-Election",
                          "apolitical" = "Apolitical",
                          "apolafterprotest" = "Apolitical x Post-Protest",
                          "apolpostelection" = "Apolitical x Post-Election"),
             title = "Table 2B: Partisan impact of the election and protest on trust",
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             add_rows = tribble(~term, ~Model,
                      "F-test", sprintf("%.2f", F.stat),
                      "F-test p-value",  sprintf("%.3f", p.val)),
             output = "kableExtra") %>% 
  kable_styling(latex_options = c("scale_down", "hold_position"))
```


### Online Appendix 3

```{r, results='asis'}
#Table 3.1

reg.3a.invite1 <- glm(invite1 ~ period3 + period2min + protestday + electday + wealth +
                        education + okrug, data = data, family = binomial(link = "probit"))

reg.3a.invite2 <- glm(invite2 ~ period3 + period2min + protestday + electday + wealth +
                        education + okrug, data = data, family = binomial(link = "probit"))

reg.3a.invite3 <- glm(invite1 ~ period3 + period2min + protestday + electday + wealth +
                        education + okrug, data = data, family = binomial(link = "probit"))

reg.3a.invite.index <- lm(invite.index ~ period3 + period2min + protestday + electday + 
                             wealth + education + okrug, data = data)

modelsummary(list("Meeting 1" = reg.3a.invite1, "Meeting 2" = reg.3a.invite2,
                  "Meeting 3" = reg.3a.invite3, "Meeting Index" = reg.3a.invite.index),
             vcov = "HC2",
             coef_map = c("period3" = "Post-Protest",
                          "period2min" = "Post-Election",
                          "protestday" = "Protest Day",
                          "electday" = "Election Day"),
             title = "Table 3.1: Effect of election and protest on meeting invitations",
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"))
```

```{r}
#Table 3.2

reg.3b.invite1 <- glm(invite1 ~ period3 + period2min + protestday + electday +
                        ur + urafterprotest + urpostelection +
                        apolitical + apolafterprotest + apolpostelection +
                        wealth + education + okrug, data   = data,
                      family = binomial(link = "probit"))

reg.3b.invite2 <- glm(invite2 ~ period3 + period2min + protestday + electday +
                        ur + urafterprotest + urpostelection +
                        apolitical + apolafterprotest + apolpostelection +
                        wealth + education + okrug, data   = data,
                      family = binomial(link = "probit"))

reg.3b.invite3 <- glm(invite3 ~ period3 + period2min + protestday + electday +
                        ur + urafterprotest + urpostelection +
                        apolitical + apolafterprotest + apolpostelection +
                        wealth + education + okrug, data   = data,
                      family = binomial(link = "probit"))

reg.3b.invite.index <- lm(invite.index ~ period3 + period2min + protestday + electday +
                            ur + urafterprotest + urpostelection + apolitical + 
                            apolafterprotest + apolpostelection + wealth + education + okrug,
                          data = data)

modelsummary(list("Meeting 1" = reg.3b.invite1, "Meeting 2" = reg.3b.invite2,
                  "Meeting 3" = reg.3b.invite3, "Meeting Index" = reg.3b.invite.index),
             vcov = "HC2",
             coef_map = c("period3" = "Post-Protest",
                          "period2min" = "Post-Election",
                          "protestday" = "Protest Day",
                          "electday" = "Election Day",
                          "ur" = "United Russia",
                          "urafterprotest" = "United Russia x Post-Protest",
                          "urpostelection" = "United Russia x Post-Election",
                          "apolitical" = "Apolitical",
                          "apolafterprotest" = "Apolitical x Post-Protest",
                          "apolpostelection" = "Apolitical x Post-Election"),
             title = "Table 3.2: Partisan impact of the election and protest on meeting invitations",
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"))

```

### Online Appendix 4

RMLS data to generate the appropriate tables are not available in the replication files.

# Supplementary robustness checks

### Calculating non-response rates by period
```{r}
# Creating data for each period
period1.data <- data %>% 
  filter(period1min == 1)

period2.data <- data %>% 
  filter(period2min == 1)

period3.data <- data %>% 
  filter(period3 == 1)

# Full sample non-response rates
nr.mean.govind <- mean(data$trustgovind.nr, na.rm = TRUE)
nr.mean.army <- mean(data$trustarmy.nr, na.rm = TRUE)
nr.mean.police <- mean(data$trustpolice.nr, na.rm = TRUE)
nr.mean.fsb <- mean(data$trustfsb.nr, na.rm = TRUE)
nr.mean.court <- mean(data$trustcourt.nr, na.rm = TRUE)
nr.mean.mungov <- mean(data$trustmungov.nr, na.rm = TRUE)
nr.mean.fedgov <- mean(data$trustfedgov.nr, na.rm = TRUE)
nr.mean.duma <- mean(data$trustduma.nr, na.rm = TRUE)
nr.mean.procuracy <- mean(data$trustprocuracy.nr, na.rm = TRUE)
nr.mean.un <- mean(data$trustun.nr, na.rm = TRUE)

# Period 1 non-response rates
p1.nr.mean.govind <- mean(period1.data$trustgovind.nr, na.rm = TRUE)
p1.nr.mean.army <- mean(period1.data$trustarmy.nr, na.rm = TRUE)
p1.nr.mean.police <- mean(period1.data$trustpolice.nr, na.rm = TRUE)
p1.nr.mean.fsb <- mean(period1.data$trustfsb.nr, na.rm = TRUE)
p1.nr.mean.court <- mean(period1.data$trustcourt.nr, na.rm = TRUE)
p1.nr.mean.mungov <- mean(period1.data$trustmungov.nr, na.rm = TRUE)
p1.nr.mean.fedgov <- mean(period1.data$trustfedgov.nr, na.rm = TRUE)
p1.nr.mean.duma <- mean(period1.data$trustduma.nr, na.rm = TRUE)
p1.nr.mean.procuracy <- mean(period1.data$trustprocuracy.nr, na.rm = TRUE)
p1.nr.mean.un <- mean(period1.data$trustun.nr, na.rm = TRUE)

# Period 2 non-response rates
p2.nr.mean.govind <- mean(period2.data$trustgovind.nr, na.rm = TRUE)
p2.nr.mean.army <- mean(period2.data$trustarmy.nr, na.rm = TRUE)
p2.nr.mean.police <- mean(period2.data$trustpolice.nr, na.rm = TRUE)
p2.nr.mean.fsb <- mean(period2.data$trustfsb.nr, na.rm = TRUE)
p2.nr.mean.court <- mean(period2.data$trustcourt.nr, na.rm = TRUE)
p2.nr.mean.mungov <- mean(period2.data$trustmungov.nr, na.rm = TRUE)
p2.nr.mean.fedgov <- mean(period2.data$trustfedgov.nr, na.rm = TRUE)
p2.nr.mean.duma <- mean(period2.data$trustduma.nr, na.rm = TRUE)
p2.nr.mean.procuracy <- mean(period2.data$trustprocuracy.nr, na.rm = TRUE)
p2.nr.mean.un <- mean(period2.data$trustun.nr, na.rm = TRUE)

# Period 3 non-response rates
p3.nr.mean.govind <- mean(period3.data$trustgovind.nr, na.rm = TRUE)
p3.nr.mean.army <- mean(period3.data$trustarmy.nr, na.rm = TRUE)
p3.nr.mean.police <- mean(period3.data$trustpolice.nr, na.rm = TRUE)
p3.nr.mean.fsb <- mean(period3.data$trustfsb.nr, na.rm = TRUE)
p3.nr.mean.court <- mean(period3.data$trustcourt.nr, na.rm = TRUE)
p3.nr.mean.mungov <- mean(period3.data$trustmungov.nr, na.rm = TRUE)
p3.nr.mean.fedgov <- mean(period3.data$trustfedgov.nr, na.rm = TRUE)
p3.nr.mean.duma <- mean(period3.data$trustduma.nr, na.rm = TRUE)
p3.nr.mean.procuracy <- mean(period3.data$trustprocuracy.nr, na.rm = TRUE)
p3.nr.mean.un <- mean(period3.data$trustun.nr, na.rm = TRUE)

# Summary table
nonresponse.tab <- data.frame(
  var.name = c("Gov't Index", "Army", "Police", "FSB", "Court", 
               "Mun Gov", "Fed Gov", "Duma", "Procuracy", "UN"),
  full.sample = c(nr.mean.govind, nr.mean.army, nr.mean.police, nr.mean.fsb, nr.mean.court,
                  nr.mean.mungov, nr.mean.fedgov, nr.mean.duma, nr.mean.procuracy, nr.mean.un),
  period1 = c(p1.nr.mean.govind, p1.nr.mean.army, p1.nr.mean.police, p1.nr.mean.fsb, p1.nr.mean.court,
              p1.nr.mean.mungov, p1.nr.mean.fedgov, p1.nr.mean.duma, p1.nr.mean.procuracy,
              p1.nr.mean.un),
  period2 = c(p2.nr.mean.govind, p2.nr.mean.army, p2.nr.mean.police, p2.nr.mean.fsb, p2.nr.mean.court,
              p2.nr.mean.mungov, p2.nr.mean.fedgov, p2.nr.mean.duma, p2.nr.mean.procuracy, 
              p2.nr.mean.un),
  period3 = c(p3.nr.mean.govind, p3.nr.mean.army, p3.nr.mean.police, p3.nr.mean.fsb, p3.nr.mean.court,
              p3.nr.mean.mungov, p3.nr.mean.fedgov, p3.nr.mean.duma, p3.nr.mean.procuracy, 
              p3.nr.mean.un),
  row.names = NULL)

nonresponse.tab
```


### Check S1: Worst-case imputation: non-responders assigned trust = 1 (maximum distrust)
```{r, results='asis'}
# Imputing NAs with 1
data.wc <- data %>% 
  mutate(trustarmy = ifelse(is.na(trustarmy), 1, trustarmy),
         trustpolice = ifelse(is.na(trustpolice), 1, trustpolice),
         trustfsb = ifelse(is.na(trustfsb), 1, trustfsb),
         trustcourt = ifelse(is.na(trustcourt), 1, trustcourt),
         trustmungov = ifelse(is.na(trustmungov), 1, trustmungov),
         trustfedgov = ifelse(is.na(trustfedgov), 1, trustfedgov),
         trustduma = ifelse(is.na(trustduma), 1, trustduma),
         trustprocuracy = ifelse(is.na(trustprocuracy), 1, trustprocuracy),
         trustun = ifelse(is.na(trustun), 1, trustun))

# Recomputing gov trust index using imputed values
data.wc <- data.wc %>% 
  mutate(trustgovind = (trustarmy + trustpolice + trustfsb + trustcourt + 
                          trustmungov + trustfedgov + trustduma +
                          trustprocuracy)/8)

# Running analysis
lm.wc.govindex <- lm(trustgovind ~ period3 + period2min + protestday + electday +
                       wealth + education + okrug, data = data.wc) 

lm.wc.army <- lm(trustarmy ~ period3 + period2min + protestday + electday +
                   wealth + education + okrug, data = data.wc) 

lm.wc.police <- lm(trustpolice ~ period3 + period2min + protestday + electday +
                     wealth + education + okrug, data = data.wc) 

lm.wc.fsb <- lm(trustfsb ~ period3 + period2min + protestday + electday +
                  wealth + education + okrug, data = data.wc) 

lm.wc.court <- lm(trustcourt ~ period3 + period2min + protestday + electday +
                    wealth + education + okrug, data = data.wc) 

lm.wc.mungov <- lm(trustmungov ~ period3 + period2min + protestday + electday +
                     wealth + education + okrug, data = data.wc) 

lm.wc.fedgov <- lm(trustfedgov ~ period3 + period2min + protestday + electday +
                     wealth + education + okrug, data = data.wc) 

lm.wc.duma <- lm(trustduma ~ period3 + period2min + protestday + electday +
                   wealth + education + okrug, data = data.wc) 

lm.wc.procuracy <- lm(trustprocuracy ~ period3 + period2min + protestday + electday +
                        wealth + education + okrug, data = data.wc) 

lm.wc.un <- lm(trustun ~ period3 + period2min + protestday + electday +
                 wealth + education + okrug, data = data.wc) 

modelsummary(list("Gov't Index" = lm.wc.govindex, "Army" = lm.wc.army, "Police" = lm.wc.police, 
                  "FSB" = lm.wc.fsb, "Court" = lm.wc.court, "Municipal Gov" = lm.wc.mungov,
                  "Federal Gov" = lm.wc.fedgov, "Duma" = lm.wc.duma, 
                  "Procuracy" = lm.wc.procuracy, "United Nations" = lm.wc.un),
             title = "Robustness Check S1: Table 2A Under Worst-Case Non-Response Imputation (missing = 1)",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
                          "period2min" = "Post-election", 
                          "protestday" = "Protest day", 
                          "electday" = "Election day"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))

```

### Robustness Check S2: Examining differences in trust item completion across respondents

```{r, results='asis'}
# Counting how many trust item questions each respondent answered
data <- data %>% 
  mutate(answered = (!is.na(trustarmy)) + (!is.na(trustpolice)) +
           (!is.na(trustfsb)) + (!is.na(trustcourt)) +
           (!is.na(trustmungov)) + (!is.na(trustfedgov)) +
           (!is.na(trustduma)) + (!is.na(trustprocuracy)))

# Building frequency table
complete.tab <- data %>% 
  group_by(answered) %>% 
  summarize(respondents = n()) %>% 
  ungroup()

complete.tab

# Building partial-response index: mean of whichever items each respondent answered

data <- data %>% 
  mutate(trustgovind.partial = rowMeans(
    cbind(trustarmy, trustpolice, trustfsb, trustcourt,
          trustmungov, trustfedgov, trustduma, trustprocuracy),
    na.rm = TRUE))

# Comparing sample sizes between models (including partial-response model)
lm.partial.govindex <- lm(trustgovind.partial ~ period3 + period2min + protestday + 
                            electday + wealth + education + okrug, data = data)

size.comp.tab <- data.frame("Model" = c("Main trust index model", 
                                       "Partial-response index model", 
                                       "Observations recovered"),
                             "Size (N)" = c(nobs(lm.govindex), 
                                            nobs(lm.partial.govindex), 
                                            nobs(lm.partial.govindex) - nobs(lm.govindex)))

size.comp.tab


# Refit all 10 trust regressions using the partial-response index
data.partial <- data %>% 
  mutate(trustgovind = trustgovind.partial)

lm.partial.govindex <- lm(trustgovind ~ period3 + period2min + protestday + electday +
                            wealth + education + okrug, data = data.partial)

lm.partial.army <- lm(trustarmy ~ period3 + period2min + protestday + electday +
                        wealth + education + okrug, data = data.partial)

lm.partial.police <- lm(trustpolice ~ period3 + period2min + protestday + electday +
                          wealth + education + okrug, data = data.partial)

lm.partial.fsb <- lm(trustfsb ~ period3 + period2min + protestday + electday +
                       wealth + education + okrug, data = data.partial)

lm.partial.court <- lm(trustcourt ~ period3 + period2min + protestday + electday +
                         wealth + education + okrug, data = data.partial)

lm.partial.mungov <- lm(trustmungov ~ period3 + period2min + protestday + electday +
                          wealth + education + okrug, data = data.partial)

lm.partial.fedgov <- lm(trustfedgov ~ period3 + period2min + protestday + electday +
                          wealth + education + okrug, data = data.partial)

lm.partial.duma <- lm(trustduma ~ period3 + period2min + protestday + electday +
                        wealth + education + okrug, data = data.partial)

lm.partial.procuracy <- lm(trustprocuracy ~ period3 + period2min + protestday + electday +
                             wealth + education + okrug, data = data.partial)

lm.partial.un <- lm(trustun ~ period3 + period2min + protestday + electday +
                      wealth + education + okrug, data = data.partial)

# Output table
modelsummary(list("Gov't Index" = lm.partial.govindex, "Army" = lm.partial.army,
                  "Police" = lm.partial.police, "FSB" = lm.partial.fsb,
                  "Court" = lm.partial.court, "Municipal Gov" = lm.partial.mungov,
                  "Federal Gov" = lm.partial.fedgov, "Duma" = lm.partial.duma,
                  "Procuracy" = lm.partial.procuracy, "United Nations" = lm.partial.un),
             title = "Robustness Check S2: Partial-response trust index (using mean of available items)",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest", 
                          "period2min" = "Post-election", 
                          "protestday" = "Protest day", 
                          "electday" = "Election day"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))

```

### Robustness Check S3: Daily mean trust plot with CI and loess smoothing

```{r}
# Build a single date variable using "MONTH" and "day" variables from original data
data <- data %>% 
  mutate(response.date = case_when(MONTH == 11 ~ as.Date(paste0("2011-11-", sprintf("%02d", day))),
                                   MONTH == 12 ~ as.Date(paste0("2011-12-", sprintf("%02d", day)))))

# Calculate daily means and 95% CIs
daily.data <- data %>% 
  group_by(response.date) %>% 
  summarize(mean.trust = mean(trustgovind, na.rm = TRUE),
            sd.trust = sd(trustgovind, na.rm = TRUE),
            size.trust = sum(!is.na(trustgovind)),
            se.trust = sd.trust / sqrt(size.trust),
            ci.lower = mean.trust - 1.96 * se.trust,
            ci.upper = mean.trust + 1.96 * se.trust) %>% 
  ungroup()

# Plotting daily trust
daily.trust.plot <- ggplot(daily.data, aes(x = response.date, y = mean.trust)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin = ci.lower, ymax = ci.upper)) +
  geom_smooth(method = "loess", se = FALSE) +
  geom_vline(xintercept = as.Date("2011-12-10"), linetype = "dashed", colour = "red") +
  labs(title = "Robustness Check S3: Daily mean trust in government",
       x = "Survey date", 
       y = "Mean trust in government")

daily.trust.plot

```

### Robustness Check S4: Placebo timing tests

```{r}
# For each date, we build a specific sub-dataset, then run a separate regression for each placebo protest date and store coefs to present together in one table

# Dec 6
data.placebo.dec6 <- data %>% 
  mutate(post.fake = ifelse(response.date > as.Date("2011-12-06"), 1, 0),
         fake.day = ifelse(response.date == as.Date("2011-12-06"), 1, 0))

lm.placebo.dec6 <- lm(trustgovind ~ post.fake + fake.day + wealth + education + okrug, 
                      data = data.placebo.dec6)
coefs.dec6 <- coeftest(lm.placebo.dec6, vcov = vcovHC(lm.placebo.dec6, type = "HC2"))

# Dec 7
data.placebo.dec7 <- data %>% 
  mutate(post.fake = ifelse(response.date > as.Date("2011-12-07"), 1, 0),
         fake.day = ifelse(response.date == as.Date("2011-12-07"), 1, 0))

lm.placebo.dec7 <- lm(trustgovind ~ post.fake + fake.day + wealth + education + okrug, 
                      data = data.placebo.dec7)

coefs.dec7 <- coeftest(lm.placebo.dec7, vcov = vcovHC(lm.placebo.dec7, type = "HC2"))

# Dec 8
data.placebo.dec8 <- data %>% 
  mutate(post.fake = ifelse(response.date > as.Date("2011-12-08"), 1, 0),
         fake.day = ifelse(response.date == as.Date("2011-12-08"), 1, 0))

lm.placebo.dec8 <- lm(trustgovind ~ post.fake + fake.day + wealth + education + okrug, 
                      data = data.placebo.dec8)

coefs.dec8 <- coeftest(lm.placebo.dec8, vcov = vcovHC(lm.placebo.dec8, type = "HC2"))

# Dec 9
data.placebo.dec9 <- data %>% 
  mutate(post.fake = ifelse(response.date > as.Date("2011-12-09"), 1, 0),
         fake.day = ifelse(response.date == as.Date("2011-12-09"), 1, 0))

lm.placebo.dec9 <- lm(trustgovind ~ post.fake + fake.day + wealth + education + okrug, 
                      data = data.placebo.dec9)

coefs.dec9 <- coeftest(lm.placebo.dec9, vcov = vcovHC(lm.placebo.dec9, type = "HC2"))

# Dec 10 (true protest date)
data.placebo.dec10 <- data %>% 
  mutate(post.fake = ifelse(response.date > as.Date("2011-12-10"), 1, 0),
         fake.day = ifelse(response.date == as.Date("2011-12-10"), 1, 0))

lm.placebo.dec10 <- lm(trustgovind ~ post.fake + fake.day + wealth + education + okrug, 
                       data = data.placebo.dec10)

coefs.dec10 <- coeftest(lm.placebo.dec10, vcov = vcovHC(lm.placebo.dec10, type = "HC2"))

# Dec 11
data.placebo.dec11 <- data %>% 
  mutate(post.fake = ifelse(response.date > as.Date("2011-12-11"), 1, 0),
         fake.day = ifelse(response.date == as.Date("2011-12-11"), 1, 0))

lm.placebo.dec11 <- lm(trustgovind ~ post.fake + fake.day + wealth + education + okrug, 
                       data = data.placebo.dec11)

coefs.dec11 <- coeftest(lm.placebo.dec11, vcov = vcovHC(lm.placebo.dec11, type = "HC2"))

# Summary table
placebo.tab <- data.frame(date = c("Dec 6", "Dec 7", "Dec 8", "Dec 9", "Dec 10", "Dec 11"),
                          post.coef = c(coefs.dec6["post.fake", "Estimate"],
                                        coefs.dec7["post.fake", "Estimate"],
                                        coefs.dec8["post.fake", "Estimate"],
                                        coefs.dec9["post.fake", "Estimate"],
                                        coefs.dec10["post.fake", "Estimate"],
                                        coefs.dec11["post.fake", "Estimate"]),
                          p.val = c(coefs.dec6["post.fake", "Pr(>|t|)"],
                                    coefs.dec7["post.fake", "Pr(>|t|)"],
                                    coefs.dec8["post.fake", "Pr(>|t|)"],
                                    coefs.dec9["post.fake", "Pr(>|t|)"],
                                    coefs.dec10["post.fake", "Pr(>|t|)"],
                                    coefs.dec11["post.fake", "Pr(>|t|)"]),
                          row.names = NULL)

placebo.tab

```

### Robustness Check S5: Assessing further heterogeneity by education

```{r}

# Create new, more fine-grained education categorical variable
data <- data %>% 
  mutate(educ.cat = case_when(education == 0 ~ 0, #no education
                              education >= 1 & education <= 3 ~ 1, #bottom 1/3
                              education >= 4 & education <= 6 ~ 2, #middle 1/3
                              education >= 7 & education <= 9 ~ 3), #highest 1/3
         educ = factor(educ.cat))


# Running regressions with interactions

lm.heteduc.govindex <- lm(trustgovind ~ period3 + period2min + protestday + electday +
                            educ.cat + educ.cat:period3 + educ.cat:period2min +
                            wealth + okrug, data = data)

lm.heteduc.army <- lm(trustarmy ~ period3 + period2min + protestday + electday +
                        educ.cat + educ.cat:period3 + educ.cat:period2min +
                        wealth + okrug, data = data)

lm.heteduc.police <- lm(trustpolice ~ period3 + period2min + protestday + electday +
                          educ.cat + educ.cat:period3 + educ.cat:period2min +
                          wealth + okrug, data = data)

lm.heteduc.fsb <- lm(trustfsb ~ period3 + period2min + protestday + electday +
                       educ.cat + educ.cat:period3 + educ.cat:period2min +
                       wealth + okrug, data = data)

lm.heteduc.court <- lm(trustcourt ~ period3 + period2min + protestday + electday +
                         educ.cat + educ.cat:period3 + educ.cat:period2min +
                         wealth + okrug, data = data)

lm.heteduc.mungov <- lm(trustmungov ~ period3 + period2min + protestday + electday +
                          educ.cat + educ.cat:period3 + educ.cat:period2min +
                          wealth + okrug, data = data)

lm.heteduc.fedgov <- lm(trustfedgov ~ period3 + period2min + protestday + electday +
                          educ.cat + educ.cat:period3 + educ.cat:period2min +
                          wealth + okrug, data = data)

lm.heteduc.duma <- lm(trustduma ~ period3 + period2min + protestday + electday +
                        educ.cat + educ.cat:period3 + educ.cat:period2min +
                        wealth + okrug, data = data)

lm.heteduc.procuracy <- lm(trustprocuracy ~ period3 + period2min + protestday + electday +
                             educ.cat + educ.cat:period3 + educ.cat:period2min +
                             wealth + okrug, data = data)

lm.heteduc.un <- lm(trustun ~ period3 + period2min + protestday + electday +
                      educ.cat + educ.cat:period3 + educ.cat:period2min +
                      wealth + okrug, data = data)

# Reporting in one table
modelsummary(list("Gov Index" = lm.heteduc.govindex, "Army" = lm.heteduc.army, 
                  "Police" = lm.heteduc.police, "FSB" = lm.heteduc.fsb, 
                  "Court" = lm.heteduc.court, "Municipal Gov" = lm.heteduc.mungov,
                  "Federal Gov" = lm.heteduc.fedgov, "Duma" = lm.heteduc.duma, 
                  "Procuracy" = lm.heteduc.procuracy, "United Nations" = lm.heteduc.un),
             title = "Robustness Check S5: Heterogeneous effects on trust by education group (reference level = 0 [no education])",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest",
                          "period2min" = "Post-election",
                          "protestday" = "Protest day",
                          "electday" = "Election day",
                          "educ.catg1" = "Education group 1 (1-3)",
                          "educ.catg2" = "Education group 2 (4-6)",
                          "educ.catg3" = "Education group 3 (7-9)",
                          "period3:educ.catg1" = "Educ Group 1 x Post-Protest",
                          "period3:educ.catg2" = "Educ Group 2 x Post-Protest",
                          "period3:educ.catg3" = "Educ Group 3 x Post-Protest",
                          "period2min:educ.catg1" = "Educ Group 1 x Post-Election",
                          "period2min:educ.catg2" = "Educ Group 2 x Post-Election",
                          "period2min:educ.catg3" = "Educ Group 3 x Post-Election"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))



```

### Robustness Check S6: Assessing further heterogeneity by state sector involvement

```{r}

# State sector is a dummy variable (respondent works in the state sector = 1)

lm.hetstate.govindex <- lm(trustgovind ~ period3 + period2min + protestday + electday +
                             statesector + statesector:period3 + statesector:period2min +
                             wealth + education + okrug, data = data)

lm.hetstate.army <- lm(trustarmy ~ period3 + period2min + protestday + electday +
                         statesector + statesector:period3 + statesector:period2min +
                         wealth + education + okrug, data = data)

lm.hetstate.police <- lm(trustpolice ~ period3 + period2min + protestday + electday +
                           statesector + statesector:period3 + statesector:period2min +
                           wealth + education + okrug, data = data)

lm.hetstate.fsb <- lm(trustfsb ~ period3 + period2min + protestday + electday +
                        statesector + statesector:period3 + statesector:period2min +
                        wealth + education + okrug, data = data)

lm.hetstate.court <- lm(trustcourt ~ period3 + period2min + protestday + electday +
                          statesector + statesector:period3 + statesector:period2min +
                          wealth + education + okrug, data = data)

lm.hetstate.mungov <- lm(trustmungov ~ period3 + period2min + protestday + electday +
                           statesector + statesector:period3 + statesector:period2min +
                           wealth + education + okrug, data = data)

lm.hetstate.fedgov <- lm(trustfedgov ~ period3 + period2min + protestday + electday +
                           statesector + statesector:period3 + statesector:period2min +
                           wealth + education + okrug, data = data)

lm.hetstate.duma <- lm(trustduma ~ period3 + period2min + protestday + electday +
                         statesector + statesector:period3 + statesector:period2min +
                         wealth + education + okrug, data = data)

lm.hetstate.procuracy <- lm(trustprocuracy ~ period3 + period2min + protestday + electday +
                              statesector + statesector:period3 + statesector:period2min +
                              wealth + education + okrug, data = data)

lm.hetstate.un <- lm(trustun ~ period3 + period2min + protestday + electday +
                       statesector + statesector:period3 + statesector:period2min +
                       wealth + education + okrug, data = data)

# Reporting in one table
modelsummary(list("Gov Index" = lm.hetstate.govindex, "Army" = lm.hetstate.army, 
                  "Police" = lm.hetstate.police, "FSB" = lm.hetstate.fsb, 
                  "Court" = lm.hetstate.court, "Municipal Gov" = lm.hetstate.mungov,
                  "Federal Gov" = lm.hetstate.fedgov, "Duma" = lm.hetstate.duma, 
                  "Procuracy" = lm.hetstate.procuracy, "United Nations" = lm.hetstate.un),
             title = "Robustness Check S6: Heterogeneous effects on trust by state sector employment",
             vcov = "HC2",
             coef_map = c("period3" = "Post-protest",
                          "period2min" = "Post-election",
                          "protestday" = "Protest day",
                          "electday" = "Election day",
                          "statesector" = "State sector",
                          "period3:statesector" = "State sector x Post-Protest",
                          "period2min:statesector" = "State sector x Post-Election"),
             stars = TRUE, fmt = 2, gof_map = c("nobs", "r.squared"),
             output = "kableExtra") %>% 
   kable_styling(latex_options = c("scale_down", "hold_position"))

```

